---
title: "T-Test Problem"
author: "Jose Torres Vargas"
date: "Spring, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
Ourdata <- read.csv(file="GSScsv.csv")
```


## Is there a difference in  average years of education (EDUC) between the those who did or did not vote in 2012 (VOTE12)?

$H_O$ There is no difference in average years of education between the ones that voted or not in 2012.

$H_A$ There is a difference in average years of education between the ones that voted or not in 2012.

Graphical Summary
```{r}
plot(EDUC~VOTE12,data=Ourdata)
```
Illustration of average educations vs people who voted or not.
Those with higher education voted more.

Numerical Summary
```{r}
favstats(EDUC~VOTE12,data=Ourdata)
```
Inference

```{r}
t.test(EDUC~VOTE12,data=Ourdata)
```

## CONCLUSION

P<.05, we reject the null hypothesis. There is a difference with those that average higher education with voting in 2012.